PDF madness

### 2022-07-10 PDF madness.Rmd
Brønnøysund pdf.
Experimenting with a Brønnøysund pdf.

>>>>

## Brønnøysund pdf
```{r}
riksmaal <- pdf_text("Data/20220001922542-1.pdf")
riksmaal
riksmaal_split <- strsplit(riksmaal, "\\n")
riksmaal_split
riksmaal_tibble <- tibble(riksmaal = riksmaal_split)
riksmaal2 <- riksmaal_tibble |> unnest_auto(col = 1)

riksmaal2$numbers <- riksmaal2$riksmaal |> str_remove_all("[^0-9]")
riksmaal2
```
